Gender, Age, and Peer Influence on Food Incentives in Schools

### 2024-02-20 outputs/paper/paper.qmd
updated next steps

Regardless of the nature of the decision-making, it is clear that incentivization works. For our next step, it is essential to consider how we can leverage incentivization to produce significant changes in behaviour on a large scale. For example, we can design reward programs that encourage people to adopt healthy habits or participate in eco-friendly practices.
To test the effectiveness of incentivization across different age groups, we may need to conduct the same study with various demographic groups. This will enable us to determine whether there are any differences in how people respond to incentives based on their age or other factors. For instance, younger people may be more motivated by incentives related to technology, while older generations may be more motivated by financial incentives.

>>>>

Regardless of the nature of the decision-making, it is clear that incentivization works. For our next step, it is essential to consider how we can leverage incentivization to produce significant changes in behaviour on a large scale. For example, we can design reward programs that encourage people to adopt healthy habits or participate in eco-friendly practices.
To test the effectiveness of incentivization across different age groups, we may need to conduct the same study with various demographic groups. This will enable us to determine whether there are any differences in how people respond to incentives based on their age or other factors. For instance, younger people may be more motivated by incentives related to technology, while older generations may be more motivated by financial incentives. To further explore the topic of children's behaviour and decision-making process, it is important to conduct more research to gain a better understanding of how children's behaviour changes over time and how it is influenced by external factors such as classmates or friends. Performing experiments on the same group of children as they age can help determine if they continue to perform in the same way and if their decision-making process changes over time. It is also important to determine the optimal age to teach children to eat and make healthier food choices and explore how schools can contribute to these decisions. Offering incentives can motivate children to make healthier choices and encourage them to stick to these choices over time. A deeper understanding of how children's behaviour evolves over time can be gained, and how we can best teach them to make healthier choices for a better life.
